No need to know: astrophysics-agnostic gravitational wave cosmology

### 2024-03-14 src/tex/ms.tex
[showyourwork] overleaf sync

After passing the simulated events through projected detector selection effects, the resulting catalog has \variable{output/num_found_events.txt}events, consistent with the numbers projected for \ac{O5} by \citet{kiendrebogo_observing_2023}.
We use the software package \texttt{GWMockCat} \citep{farah_things_2023} to simulate posterior samples for these events with measurement uncertainties typical of those expected from \ac{O5} detectors.
\texttt{GWMockCat} also simulates a set of software injections, which we use to estimate selection effects in the inference.
To determine the detectability of both injections and simulated events in O5, we use the projected \ac{O5} LIGO power spectral density \citep{dccpage} to calculate observed signal-to-noise ratios $\rho_{\text{obs}}$, and we consider events and injections with $\rho_{\text{obs}}>8$ to be detectable. 
The full procedure for this mock data generation process is described in \citet{fishbach_where, farah_things_2023, essick_dagnabbit_2023}, and the exact settings used for \texttt{GWMockCat} are made available in the accompanying data release.

>>>>

After passing the simulated events through projected detector selection effects, the resulting catalog has $\variable{output/num_found_events.txt}$ events, consistent with the numbers projected for \ac{O5} by \citet{kiendrebogo_observing_2023}.
We use the software package \texttt{GWMockCat} \citep{farah_things_2023} to simulate posterior samples for these events with measurement uncertainties typical of those expected from \ac{O5} detectors.
\texttt{GWMockCat} also simulates a set of software injections, which we use to estimate selection effects in the inference.
To determine the detectability of both injections and simulated events in O5, we use the projected \ac{O5} LIGO power spectral density \citep{dccpage} to calculate observed signal-to-noise ratios $\rho_{\text{obs}}$, and we consider events and injections with $\rho_{\text{obs}}>8$ to be detectable. 
The full procedure for this mock data generation process is described in \citet{fishbach_where, farah_things_2023, essick_dagnabbit_2023}, and the exact settings used for \texttt{GWMockCat} are made available in the accompanying data release.
